Literature

### 2017-08-28 Thesis/Draft.tex
Edit AugUCB chapter

@@

In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
its first argument, and thus can be relatively well approximated by
Pinsker's inequality (SHOW IN GRAPH!):

@@

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{sec:VarianceBasedAlgorithms}.

\includegraphics{Draft_files/figure-latex/unnamed-chunk-2-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-3-1.pdf}

@@

where \(\bm{\lambda}\) is the vector of means defining the distributions
of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
probability distributions on the arms \(\mathcal{A}\):
\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\).
\marginpar{Give more intuition for what these probability distributions are}
We are now ready to state the theorem.

@@

\section{Extensions to the Thresholding Bandit
Problem}\label{extensions-to-the-thresholding-bandit-problem}

\subsection{Introduction}\label{introduction-1}

We have introduced the thresholding bandit problem in chapter 1. The APT
algorith described in Locatelli et al. (2016) is able to match a lower
bound (be more specific!) given in the same paper, and has several
favorable characteristics such as its overall simplicity and it being an
anytime algorithm. However, the bounds on the expected loss assume the
arms' distributions to be \(R\)-sub-Gaussian. This is reflected in the
algorithm's complexity measure
\(H = \sum_{i=1}^K (\Delta_i^{\tau, \epsilon})^{-2}\), where
\(\Delta_i^{\tau,\epsilon} = |\mu_i - \tau| + \epsilon\), which -- given
the known threshold \(\tau \pm \epsilon\) -- only depends on the
distribution's mean. This is appropriate for Gaussian arms with equal
variances, but potentially inefficient for other kinds of distributions.

@@

In the case of Gaussians, the complexity \(H\) is nice also because it
reflects the Kullback-Leibler divergence between two Gaussians. And
since Bernoulli distributions are bounded on the interval \([0,1]\),
they are consequently sub-Gaussian, meaning that their Kullback-Leibler
divergence can be approximated by the Gaussian one. However, while
Bernoullis are sub-Gaussian, the approximation of their divergence by
the Gaussian divergence becomes less and less optimal as the parameter
(and thus mean) goes to \(0\) or \(1\), as shown in chapter 1. And while
online advertisements might not be an obvious use case for thresholding
bandits, they are just one real life scenario dominated by Bernoulli
distributions with very small parameters. Thus it is worthwile to adapt
current solutions of the thresholding bandit problem to cases in which
the Gaussian Kullback-Leibler divergence is no longer an appropriate
approximation.

Large motiviation for the idea of adjusting the complexity measure (and
thus the algorithms) to distributions more generally based on the
Kullback-Leibler divergence stems from the work discussed in chapter 2,
complexity measures were defined for the pure exploration bandits in
terms of the Kullback-Leibler divergence. Based on this, the authors
were for example able to point our differences between Gaussian and
Bernoulli bandits. We expect that results in a similar vain could be
derived for thresholding bandits.

To this end, in the following, we first present an extension of mean
based algorithms to an algorithm that incorporates empirical variances
as described in Mukherjee et al. (2017). Afterwards, we propose and
discuss potential further improvements based on Kullback-Leibler
divergence and Bayesian posterior distributions. Finally, we compare the
performance of different algorithms based on simulations and real world
data sets.

\subsection{\texorpdfstring{Variance Based Algorithms for Thresholding
Bandits
\label{chap:VarianceBasedAlgorithms}}{Variance Based Algorithms for Thresholding Bandits }}\label{variance-based-algorithms-for-thresholding-bandits}

@@

Mukherjee et al. (2017) propose an algorithm based on variance estimates
called Augmented-UCB (AugUCB). The setting in which the algorithm is
proposed is very similar to the setting in Locatelli et al. (2016). The
algorithm itself, however, differs heavily from the APT algorithm. So is
AugUCB for example not an anytime algorithm. Furthermore, arms can be
deleted in every round if there are ``far enough'' away from the mean.
Both the decision of which arm is played in a given round, and whether
an arm is removed from the active set of arm, is based not only on the
empirical mean estimate \(\mu_i(t)\), but also on a term \(s_i\) that is
increasing linearly in the estimated standard deviation. While the APT
algorithm plays the arm minimizing the quantity
\(B_i(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
AugUCB plays the arm minimizing the quantity
\((\hat{\Delta}_i(t) - 2s_i)\), where \(s_i\) is based on the variance
estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
\(T\), and an elimination parameter \(\rho\) (compare Algorithm 1 in
Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}
\end{equation*}

Consequently, the authors also introduce complexity measures which take
the variance into account. From Gabillon et al. (2011) they use
\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
Furthermore, with
\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
and with \(\stackrel{\sim}{\Delta}_{(i)}\) being an increasing ordering
of \(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \ in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the
AugUCB algorithm's expected loss, it could be replaced by
\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
\(H_{\sigma,1}\) is of course more directly comparable to the complexity
\(H\) that we are used to.

While in the case of the APT algorithm the number of times a specific
arm has been drawn \(T_i\) measures how concentrated the estimated mean
is around the true mean (and thus for large \(T_i\) an arm is no longer
drawn even if \(\hat{\mu}\) is close to \(\tau\)); in the case of the
AugUCB algorithm this is regulated by the combination of the variance
estimate \(\hat{v}_i\) and the exploration factor \(\psi_m\), where they
ensure that certain arms are no longer pulled when the algorithm is
sufficiently confident in its knowledge about the true mean. Therefore,
when using a very similar favorable event in the proof of their upper
bound, Mukherjee et al. (2017) have to bound the probability that an an
arm is not removed from the active set after the a certain number of
rounds -- even though the arm is above (respectively below) the
threshold. If this probability is low, then this means that the
algorithm is able to be certain about an arm's true mean \emph{quickly}
by employing variance estimates. In comparison, Locatelli et al (2016)
used bounds on on how often arms are drawn (\(T_i\)) to give a bound on
the probability of the favorable event. In order to derive the bound,
Mukherjee et al. (2017) use the Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the
distributions have rewards bounded in \([0,1]\) in order to derive the
bound on the probability that an arm has not been eliminated correctly
in round \(T_i\). Thus, the distributions for which their upper bound
holds are a subset of the sub-Gaussian distributions considered in
Locatelli et al. (2016). However, it is not that the authors need to
assume that the rewards are in \([0,1]\), but this was assumed so that
the variance of the distribution is in \([0,1]\). Thus, the upper bound
holds in particular for Gaussian distributions with variance
\(\sigma^2 \in [0,1]\).

@@

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
that the left part of the RHS gives the probability that the mean
estimate is out of wack, while the right term gives the probability that
the variance is overestimated. The first term is bounded by the
Bernstein inequality. In the cumulative regret setting, there exists a
similar decomposition that bounds the expected number of pulls of a
suboptimal arm. Compare for example chapter 3.1 in ``Thompson Sampling:
An Asymptotically Optimal Finite Time Analysis'' by Kaufmann, Korda and
Munos (2012). There they decompose the expected number of draws of an
suboptimal arm for an optimistic (UCB like) into the probability that
the optimal arm's mean is underestimated, and the probability that the
UCB of the suboptimal arm is still very large. To give bounds for UCB
algorithms, it is then shown that these two terms show a certain
convergence. Mukherjee et al. do similarly for their variance based
algorithm in the thresholding setting.

(since the AugUCB eliminates arms, it is interesting to see how it
behaves when the underlying CTR changes over time\ldots{})

-\textgreater{} Happens for exponential distribution

@@

\includegraphics{Draft_files/figure-latex/EVT_Index_Bernoulli-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/Hevt_Hapt_Comparison-1.pdf}

@@

\section{Experiments}\label{experiments}

\subsection{Synthetic Data}\label{synthetic-data}

@@

\includegraphics{Draft_files/figure-latex/simulation1_results-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/simulation2_results-1.pdf}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}
\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-2.pdf}

@@

\includegraphics{Draft_files/figure-latex/simulation3_results-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/simulation4_results-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/simulation5_results-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-1.pdf}
\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-2.pdf}
\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-3.pdf}
\includegraphics{Draft_files/figure-latex/unnamed-chunk-8-4.pdf}

\includegraphics{Draft_files/figure-latex/unnamed-chunk-9-1.pdf}

@@

\includegraphics{Draft_files/figure-latex/unnamed-chunk-10-1.pdf}

@@

The authors thank Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
for many hours of valuable feedback and ideas. \textless{}3

>>>>

\begin{itemize}
\tightlist
\item
  Mention Optimality (Upper Bound matches lower bound)
\item
  Anytime
\end{itemize}

@@

In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
its first argument, and thus can be relatively well approximated by
Pinsker's inequality:

@@

In what follows, we first examine in
\autoref{chap:KullbackLeiblerPureExploration} how information theoretic
quantities are employed in the best arm identification and Top-\(m\)
problem as detailed in Kaufmann and Garivier (2016) and Kaufmann et al.
(2016). Before introducing a new algorithm for the thresholding bandit
problem based on Kullback-Leibler divergences in
\autoref{sec:LikelihoodRatioForExponentialFamily}, we first describe the
variance-based approaches in \autoref{chap:VarianceBasedAlgorithms}.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/KLApproximationComparison-1}

}

\caption{The approximation of the Bernoulli KL-divergence by the Gaussian KL-divergence works well if the second argument is equal to 0.5. Else we observe poor approximation in both value and symmetry. This becomes more obvious as the arguments move away from 0.5.}\label{fig:KLApproximationComparison}
\end{figure}

@@

@@

where \(\bm{\lambda}\) is the vector of means defining the distributions
of the alternative problem to \(\bm{\mu}\). Lastly, we have the set of
probability distributions on the arms \(\mathcal{A}\):
\(\Sigma_K = \{w \in \mathbb{R}_{+}^K: w_1 + \dots + w_K = 1\}\). We are
now ready to state the theorem.

@@

\section{\texorpdfstring{Extensions to the Thresholding Bandit Problem
\label{chap:Extensions}}{Extensions to the Thresholding Bandit Problem }}\label{extensions-to-the-thresholding-bandit-problem}

\subsection{\texorpdfstring{Introduction
\label{sec:ExtensionsIntroduction}}{Introduction }}\label{introduction-1}

In \autoref{chap:ThresholdingBanditProblem} we have introduced the
thresholding bandit problem as proposed in Locatelli et al. (2016)
alongside the APT algorithm. We have seen that the upper bound on the
APT algorithm matches the lower bound for the thresholding bandit
problem given in Locatelli et al. (2016). The algorithm also exhibits
favorable characteristics such that its upper bound holds at any
stopping time, and that it does not require any parameter to be known
upfront. However, we have seen that the index and the complexity term
\(H\) employed by the APT algorithm are the most effective for
\(R\)-sub-Gaussian distributions. Both are related to the KL-divergence
between two Gaussian distributions of equal variance. Given that this
sub-Gaussian approximation can be poor in certain cases, we motivated
the use of information theoretic measures in an algorithm's index
(compare \autoref{sec:DiscussionLocatelli}).

Another goal can be to compare the distributions with the threshold
based not only on the empirical mean -- as done by the APT algorithm. A
logical extension is for example the empirical variance. After all arms
do not necessarily have the same variance, even if they are
sub-Gaussian. And given two arms for which we estimate the same mean, we
would prefer to draw more samples from the arm with the larger variance.

@@

For these reasons, in the following, we first present in
\autoref{sec:VarianceBasedAlgorithms} two algorithms which incorporate
empirical variances as described in Mukherjee et al. (2017) and Zhong et
al. (2017). We then introduce a new algorithm based on the concept of
likelihood ratios in \autoref{sec:LikelihoodRatioForExponentialFamily}.
Finally, we compare the performance of different algorithms based on
simulations and real world data sets in \autoref{chap:Experiments}.

\subsection{\texorpdfstring{Variance Based Algorithms for the
Thresholding Bandit
\label{sec:VarianceBasedAlgorithms}}{Variance Based Algorithms for the Thresholding Bandit }}\label{variance-based-algorithms-for-the-thresholding-bandit}

@@

Combining learnings from the APT and other algorithms, Mukherjee et al.
(2017) propose the Augmented-UCB (AugUCB) algorithm based on variance
estimates for the thresholding bandit problem. The setting they consider
is thus very similar to the setting in Locatelli et al. (2016). The main
difference being that, while Locatelli et al. (2016) assume
\(R\)-sub-Gaussian reward distributions, Mukherjee et al. (2017) assume
rewards to be bounded in \([0,1]\), which makes the AugUCB applicable to
less distributions. The AugUCB algorithm itself differs significantly
from the APT algorithm. The two main ideas it employs are first, upper
confidence bounds based on the Bernstein inequality and empirical
variance estimates to compute the index based on which an arm is chosen
at every round. Second, if an arm estimate is ``far enough away'' from
the threshold as measured by the confidence bounds, it will be
``eliminated'', and no longer be pulled until the end of the budget.
Both ideas are based not only on the empirical mean estimate
\(\mu_i(t)\), but also on a term \(s_i\) that is increasing linearly in
the estimated standard deviation. While the APT algorithm plays the arm
minimizing the quantity
\(B_i^{APT}(t+1) = \sqrt{T_i(t)} \hat{\Delta}_i(t) = \sqrt{T_i(t)} (|\hat{\mu}_i(t) - \tau| + \epsilon)\),
AugUCB plays the arm minimizing the quantity
\(\hat{\Delta}_i(t) - 2s_i\), where \(s_i\) is based on the variance
estimate \(\hat{v}_i\), and an exploration \(\psi_m\) term linear in
\(T\), as well as an elimination parameter \(\rho\) (compare Algorithm 1
in Mukherjee et al., 2017):

\begin{equation*}
s_i = \sqrt{\frac{\rho \psi_m (\hat{v}_i + 1) \log(T \epsilon_m)}{4n_i}}.
\end{equation*}

Consequently, the authors also introduce complexity measures which take
the variance into account. From Gabillon et al. (2011) they use
\(H_{\sigma, 1}= \sum_{i=1}^K \frac{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}{\Delta_i^2}\).
Furthermore, with
\(\stackrel{\sim}{\Delta}_i^2 = \frac{\Delta_i^2}{\sigma_i + \sqrt{\sigma_i^2 + (16/3)\Delta_i}}\),
where \(\stackrel{\sim}{\Delta}_{(i)}\) is an increasing ordering of
\(\stackrel{\sim}{\Delta}_i\), the authors define a complexity
corresponding to \(H_{CSAR,2}\) in Chen et al. (2014):

\begin{equation*}
H_{\sigma,2} = \max_{i \in \mathcal{A}} \frac{i}{\stackrel{\sim}{\Delta}_{(i)}^2}.
\end{equation*}

While the latter complexity appears in the provided upper bound on the
AugUCB algorithm's expected loss, it could be replaced by
\(H_{\sigma, 1}\) since \(H_{\sigma, 2} \leq H_{\sigma,1}\).
\(H_{\sigma,1}\) is more easily compared to the complexity \(H\) defined
in Locatelli et al. (2016). Essentially, every arm's complexity
contribution is additionally scaled by a term increasing in the arm's
variance (see also the graph comparing the complexity terms of APT,
AugUCB, and EVT algorithms below).

In the case of the APT algorithm the number of times a specific arm has
been drawn \(T_i\) measures how concentrated the estimated mean is
around the true mean (and thus for large \(T_i\) an arm is no longer
drawn even if \(\hat{\mu}\) is close to \(\tau\)). This exploration is
regulated by the combination of the variance estimate \(\hat{v}_i\) and
the exploration factor \(\psi_m\) in the case of the AugUCB algorithm.
The terms ensure that certain arms are no longer pulled when the
algorithm is sufficiently confident in the location of true mean.
Indeed, the AugUCB algorithm goes a little further than the APT
algorithm in that it eliminates arms (no longer considers them in
sampling) when a separation condition is estimated to hold. The same
separation condition of estimated mean away from the threshold is used
in the authors' upper bound proof and is reminiscient of the separation
condition used in Locatelli et al.'s (2016) upper bound proof.

Therefore, when using a very similar favorable event in the proof of
their upper bound, Mukherjee et al. (2017) have to bound the probability
that an an arm is not removed from the active set after the a certain
number of rounds -- even though the arm is above (respectively below)
the threshold. If this probability is low, then the algorithm is able to
be certain about an arm's true mean by employing variance estimates. In
comparison, Locatelli et al (2016) used bounds on on how often arms are
drawn (\(T_i\)) to give a bound on the probability of the favorable
event. In order to derive the bound, Mukherjee et al. (2017) use the
Bernstein inequality.

It has to be noted that Mukherjee et al. (2017) have to assume that the
distributions have rewards bounded in \([0,1]\) in order to derive the
bound on the probability that an arm has not been eliminated correctly
in round \(T_i\). Else it would not be possible to upper bound the
\(s_i\) term by \(\Delta_i/4\) as Mukherjee et al. do in their proof.
Thus, the distributions for which their upper bound holds are a subset
of the \(R\)-sub-Gaussian distributions considered in Locatelli et al.
(2016). However, while the authors demand in their setting that the
rewards are bounded in \([0,1]\), it seems that the upper bound only
requires the arms' variances to be bounded in \([0,1]\) such that
\(\hat{v}_i \in [0,1]\). Thus, the upper bound should hold in particular
for Gaussian distributions with variance \(\sigma^2 \in [0,1]\).
Consequently, the simulations by Mukherjee et al. are performed on
Gaussian arms with variance smaller than one.

@@

Compare Mukherjee et al. (2017) for the notation. Then it becomes clear
that the left part of the RHS gives the probability that the mean
estimate is out of wack, while the right term gives the probability that
the variance is overestimated. The first term is bounded by the
Bernstein inequality. In the cumulative regret setting, there exists a
similar decomposition for algorithms based on upper confidence bounds.
There, the expected number of pulls of a suboptimal arm is bounded.
Compare for example chapter 3.1 in Kaufmann, Korda and Munos (2012), in
which the authors decompose the expected number of draws of an
suboptimal arm into the probability that the optimal arm's mean is
underestimated, and the probability that the upper confidence bound of
the suboptimal arm is still very large. To give bounds for UCB
algorithms, certain convergence rates are shown for these two
probabilities. Mukherjee et al. do similarly for their upper confidence
algorithm in the thresholding setting.

@@

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/EVT_Index_Bernoulli-1}

}

\caption{This graph displays the distance part of the index of the APT, SLR, and EVT algorithms. While EVT's distance is based on both the empirical mean and empirical variance, the empirical mean determines the variance in the case of Bernoullis. We see that the distance of both EVT and SLR has an asymmetric behavior.}\label{fig:EVT_Index_Bernoulli}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/Hevt_Hapt_Comparison-1}

}

\caption{This graph compares the complexity terms used in the APT, AugUCB, and EVT algorithms respectively. We observe that as the mean of the arm's distribution is closer to the threshold, the complexity of the problem increases much less rapidly for the EVT algorithm. Thus, the EVT should be able to cope with arms close to the threshold better than the APT algorithm. The complexity displayed for the AugUCB is an upper bound on the complexity used in the upper bound of Mukherjee et al. (2017).}\label{fig:Hevt_Hapt_Comparison}
\end{figure}

@@

\section{\texorpdfstring{Experiments
\label{chap:Experiments}}{Experiments }}\label{experiments}

\subsection{\texorpdfstring{Synthetic Data
\label{sec:SyntheticData}}{Synthetic Data }}\label{synthetic-data}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation1_results-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation2_results-1} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-3-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation3_results-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation4_results-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/simulation5_results-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-5-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-6-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-1} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-2} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-3} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-7-4} \end{center}

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-8-1} \end{center}

@@

\begin{center}\includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-9-1} \end{center}

@@

The author thanks Alexandra Carpentier, Andrea Locatelli, and Urun Dogan
for many hours of valuable feedback and ideas. \textless{}3

### 2017-08-28 Thesis/Literature.Rmd
Rewritten Setup
add hoeffding bound
Edit AugUCB chapter

@@

>>>>

Bubeck, S. and Cesa-Bianchi, N. (2012). Regret analysis of stochastic and nonstochastic multi-armed bandit problems. Foundations and Trends in Machine Learning 5 1–122.

@@

Zhong et al. (2017)

Bubeck, Sébastien, Cesa-Bianchi, Nicolo, and Lugosi, Gábor. Bandits with heavy tail. Information Theory, IEEE Transactions on, 59(11):7711-7717, 2013a.

Mukherjee et al. (2017)

Victor Gabillon, Mohammad Ghavamzadeh, Alessandro Lazaric, and Sébastien Bubeck. Multi-bandit best arm identification. In *Advances in Neural Information Processing Systems, pages 2222-2230, 2011.

Shouyuan Chen, Tian Lin, Irwin King, Michael R Lyu, and Wei Chen. Combinatorial pure exploration of multi-armed bandits. In *Advances in Neural Information Processing Systems, pages 379-387, 2014.

"Thompson Sampling: An Asymptotically Optimal Finite Time Analysis" by Kaufmann, Korda and Munos (2012)

Lihong Li, Wei Chu, John Langford, Robert E. Schapire. A Contextual-Bandit Approach to Personalized News Article Recommendation. WWW 2010, April 26–30, 2010, Raleigh, North Carolina, USA. ACM 978-1-60558-799-8/10/04.
